Cudele: A File System with Programmable Consistency and Durability

### 2017-03-31 paper/sections/3_posix_overheads.tex
paper: fix creates motivation graph
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{figures/creates-motivation.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of CephFS
.}\label{fig:creates-motivation}
\end{figure}

@@

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underyling storage system the most.
Figure~\ref{fig:creates-motivation} shows the resource utilization of compiling
the Linux kernel.  The untar phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journalling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of CephFS
.}\label{fig:overhead-creates}
\end{figure}

@@

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underyling storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The untar phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journalling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.
